New Biomass Pools Workflow

### 2023-10-04 NewBiomassPoolsWorkflow.Rmd
fixed lg_phy, ready to go

@@

  pooltype <- fgs |>
    dplyr::select(species=name, grouptype) |>
    dplyr::mutate(pooltype = dplyr::case_when((grouptype %in% c("lg_inf",
                                                                "sm_inf",
                                                                "sed_bact",
                                                                "sed_ep_ff",
                                                                "sed_ep_other",
                                                                "mobile_ep_other",
                                                                "coral",
                                                                "sponge")) ~ "benthos",
                                              TRUE ~ "nonbenth"))

@@

    pooln <- pooln |>
      dplyr::mutate(atoutput = dplyr::case_when(pooltype == "nonbenth" ~ vol * atoutput * bio_conv,
                                                pooltype == "benthos" ~ 
                                                  ifelse(layer==sedlayer, area * atoutput * bio_conv, 0)))

@@

Joe pointed out that benthic groups should be expanded to area rather than volume. That correction has now been applied, and matches are better, but still diverge over time for some groups.

Groups that match seem more likely to be pelagic (dinoflagellates, all zooplankton, pelagic bacteria, labile and refractive detritus) although large phytoplankton is way off.

@@

This is mismatch coded as 0 if less than 1% of txt output, 1 if more. Those exceeding are carrion, predatory benthos, detritivore benthos, king crab, benthic bacteria, large phytoplankton and sometimes small zooplankton.

@@

What is up with the phytoplankton groups? Small matches well visually but large doesn't. Large phytoplankton is the largest magnitude mismatch across all groups.

@@

Predatory benthos is off by what appears to be a scalar, Detrivore ben converges as they increase.

@@

BUT. Diatoms are still off so this calculation may not be working for that category.

What is up with the phytoplankton groups? Small matches well visually but large doesn't. Large phytoplankton is the largest magnitude mismatch across all groups.

>>>>

With the following exceptions!

Benthic groups have N expanded to area

LG_PHY type has N expanded to only water column, not sediment layers.

@@

   pooltype <- fgs |>
    dplyr::select(species=name, grouptype) |>
    dplyr::mutate(pooltype = dplyr::case_when((grouptype %in% c("lg_inf",
                                                                "sm_inf",
                                                                "sed_bact",
                                                                "sed_ep_ff",
                                                                "sed_ep_other",
                                                                "mob_ep_other",
                                                                "coral",
                                                                "sponge")) ~ "benthos",
                                              (grouptype %in% c("lg_phy")) ~ "lg_phy",
                                              TRUE ~ "alllayers"))

@@

    pooln <- pooln |>
      dplyr::mutate(atoutput = dplyr::case_when(pooltype == "alllayers" ~ vol * atoutput * bio_conv,
                                                pooltype == "lg_phy" ~
                                                  ifelse(layer!=sedlayer, vol * atoutput * bio_conv, 0),
                                                pooltype == "benthos" ~
                                                  ifelse(layer==sedlayer, area * atoutput * bio_conv, 0)))

@@

Joe pointed out that benthic groups should be expanded to area rather than volume. That correction has now been applied, and matches are better, but still diverge over time for some groups. Not enough to worry about I think.

Originally, large phytoplankton was way off, but Joe also pointed out that LG_PHY N can be in the sediment layer but shouldn't "count" as biomass. Therefore, this group is expanded to all layers but the sediment layer and that creates a much better match.

@@

This is mismatch coded as 0 if less than 1% of txt output, 1 if more.

@@

Large phytoplankton formerly had the largest magnitude mismatch across all groups, now fixed by not expanding N in the sediment layer for this group type.

@@

These groups seem close enough to me now.

@@

With corrections for LG_PHY things now line up in both models.
